MSE for rank_1 simulation

### 2018-01-10 analysis/MSErank1sim.Rmd
Files commited by wflow_commit.

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_sparse.rds")
colnames(sparse_res) = c("PMD","flash","SFA","SFAmix","SVD","SSVD")
boxplot(sparse_res,main = "sparse case")
```

@@

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_itermediate.rds")
colnames(sparse_res) = c("PMD","flash","SFA","SFAmix","SVD","SSVD")
boxplot(sparse_res,main = "intermediate sparse case")
```

>>>>

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_sparse.rds")
colnames(sparse_res) = c("PMD","flash","SFA","SFAmix","SVD","SSVD")
sparse_diff = sparse_res - sparse_res[,2]

boxplot(sparse_res,main = "sparse case")
boxplot(sparse_diff,main = "sparse case (difference)")
abline(a = 0,b = 0,col= "red")
```

@@

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_itermediate.rds")
colnames(sparse_res) = c("PMD","flash","SFA","SFAmix","SVD","SSVD")
sparse_diff = sparse_res - sparse_res[,2]
boxplot(sparse_res,main = "intermediate sparse case")
boxplot(sparse_diff,main = "sparse case (difference)")
abline(a = 0,b = 0,col= "red")
```
